A thermodynamic view of dusty protoplanetary disks

### 2017-06-12 linear.tex
local save

In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi&\equiv \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta
  P\Delta\rho^*\right).\notag 
%\notag\\
%       &= \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta\rhog^*\Delta\rhod\right).\notag
\end{align*}

(Note that $\Delta P = \delta P + \ii \dd v_x \p_rP/\sigma$, and it is
important to include the global radial pressure gradient here.) Then
$\varphi > 0 $ indicates gas pressure lagging behind total density,
which is true for all the cases. Thus SI is indeed associated with
such a phase lag.

>>>>

In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi&\equiv \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta
  P\Delta\rho^*\right).\notag 
%\notag\\
%       &= \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta\rhog^*\Delta\rhod\right).\notag
\end{align*}
(Note that $\Delta P = \delta P + \ii \dd v_x \p_rP/\sigma$, and it is
important to include the global radial pressure gradient here.) Then
$\varphi > 0 $ indicates gas pressure lagging behind total density,
which is true for all the cases. Thus SI is indeed associated with
such a phase lag.
